---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = "", message = FALSE, warning = FALSE)
knitr::opts_chunk$set(cache=TRUE) 
```

```{r pkg}
library(pacman)
p_load(ggplot2, dplyr, broom, magrittr, rvest, janitor, tidyr, patchwork, leaflet, sf, stringr, htmlwidgets, data.table)
```

# Airbnb Listings in Paris

<!-- badges: start -->

<!-- badges: end -->

| I aggregate data from the Inside Airbnb initiative (see below) for over 50,000 individual listings in Paris to find the total number of listings by *arrondissement* (i.e., district). In turn, I use webscraped data of the population of each arrondissement to find the density of listings for every 1000 people and by square kilometre. Lastly, I also find the average nightly rate in each area, and plot all these aggregations in interactive maps using `leaflet`.

## Data cleaning and wrangling

-   Load data from Inside Airbnb (one dataset for individual lisitings and one with the spatial coordinates of each arrondissement)


```{r load-data-from-source, message=FALSE, warning=FALSE, echo=TRUE, quiet=TRUE}
# Load data for individual listings from website
paris_listings <- fread(
  'http://data.insideairbnb.com/france/ile-de-france/paris/2022-09-09/visualisations/listings.csv')

# Read in shapefile of neighbourhoods and create sf object
paris_nhoods_geodata <- 
  st_read(here::here("data", "paris_neighbourhoods.nosync.geojson"), quiet = TRUE) %>% 
  # Get rid of unsused variables
  select(-neighbourhood_group)

```

-   Clean and aggregate data by *arrondissement*

```{r clean1, warning=FALSE, echo=TRUE}
# Get rid of dollar sign in price variable, and convert to numeric 
paris_listings$price <- as.integer(gsub("\\$", "", paris_listings$price))
```

```{r aggregate-data}
# Aggregate number of listings and average prices by arrondissement/neighbourhood
paris_list_and_avgP_nhood <- paris_listings %>% 
                                # get rid of listings with no price
                                subset(!(is.na(price))) %>% 
                                # group data by neighbourhood/arrondissement
                                group_by(neighbourhood) %>%
                                # create new column with price avg in each neighborhood
                                summarise(n_listings = n(), 
                                          avg_price = mean(price)) %>% 
                                # round prices to 0 decimal points
                                mutate(across(avg_price, round, 0))


# aggregate(price ~ neighbourhood_cleansed, data = paris_listings, function(x){sum(is.na(x))}, na.action = NULL)
```

-   Webscrape data for population and area of each arrondissement (will be used to find listings by population and by area)

```{r webscrape-paris, echo=TRUE}
# Read html address with arrondissements data from wikipedia (in italian)
wiki_paris_it <- 
  read_html("https://it.wikipedia.org/wiki/Arrondissement_municipali_di_Parigi")

## Scrape table with data for each arrondissement
paris_arronds_it <- wiki_paris_it %>% 
  html_element(".wikitable :nth-child(1)") %>%
  html_table() %>% 
  clean_names() %>% 
  select(arr, nome, superficie_ha, 
         popolazione_municipale_per_il_2010_e_2015_7, 
         densita_di_popolazione_abitanti_km2_7) %>% 
  slice(-c(1, 22, 23, 24)) %>% 
  mutate(nome = ifelse(nome == "Elyseo", "Élysée", nome),
         area_km2 = as.numeric(superficie_ha) / 100) %>% 
  rename(neighbourhood = nome,
         area_ha = superficie_ha,
         pop_2017 = popolazione_municipale_per_il_2010_e_2015_7,
         dens_2017 = densita_di_popolazione_abitanti_km2_7)

```

-   Merge aggregated listings data with webscraped data

```{r merge-data, echo=TRUE}
# Merge aggregated listings data with arrondissements data
paris_arronds_full <- merge(paris_list_and_avgP_nhood, paris_arronds_it, 
                            by.x = "neighbourhood", by.y = "neighbourhood")
```

-   Create new variables for listings population and by area:
    -   Listings per 1000 inhabitants

    -   Listings per square kilometre

```{r calc-new-vars-paris, echo=TRUE}
# Create new variables for listings and price by km2 and by population

## Calculate listings per 1000 people
  # Get rid of empty space in population column & convert variable to numeric class
paris_arronds_full$pop_2017 <- as.numeric(
  str_replace(paris_arronds_full$pop_2017,"\\s", ""))
  # Now create new variable for listings by population (and round new values)
paris_arronds_full %<>% 
  mutate(listings_by_pop = (n_listings)/(pop_2017)*1000, 
         listings_by_pop = round(listings_by_pop))


## Calculate listings per km2
paris_arronds_full %<>% mutate(listings_km2 = (n_listings)/(area_km2),
                               listings_km2 = round(listings_km2))

```

-   Merge aggregated data with geospatial data

```{r merge-agg-and-geo-data, echo=TRUE}
# Merge geospatial data (sf object) with lyon airbnb listings data
paris_merged <- merge(paris_arronds_full, paris_nhoods_geodata, 
                      by.x = "neighbourhood", by.y = "neighbourhood")

# Convert new dataframe into an sf object
paris_merged_sf <- st_as_sf(paris_merged) #%>% st_transform(8857)

```

## Static Maps:

```{r}
# Plot
ggplot() +
  geom_sf(data = paris_merged_sf, aes(fill = n_listings)) + #, col = "grey40"
  labs(title = "Total Airbnb Listings in Paris",
       subtitle = "By arrondissement",
       fill = "Listings") +
  viridis::scale_fill_viridis() +
 # coord_sf(datum = NA) +
  cowplot::theme_map()
```

```{r}
# Plot
ggplot() +
  geom_sf(data = paris_merged_sf, aes(fill = listings_by_pop)) + #, col = "grey40"
  labs(title = "Airbnb Listings for every 1000 inhabitants",
       #subtitle = "Listings for every 1000 people",
       fill = "Listings") +
  viridis::scale_fill_viridis() +
 # coord_sf(datum = NA) +
  cowplot::theme_map()
```

```{r}
# Plot
ggplot() +
  geom_sf(data = paris_merged_sf, aes(fill = listings_km2)) + #, col = "grey40"
  labs(title = "Airbnb Listings per Square KM",
      # subtitle = "Listings per square KM",
       fill = "Listings") +
  viridis::scale_fill_viridis() +
 # coord_sf(datum = NA) +
  cowplot::theme_map()
```

## Interactive Plots

```{r create-objs-for-leaflet}
### Create objects for leaflet (interactive map) icons

# Create data for landmark icons
landmarks_coords <- sp::SpatialPointsDataFrame(
  cbind(c(2.2945, 2.295, 2.3507, 2.3380, 2.3346),        # lng
        c(48.8583, 48.8738, 48.8527, 48.8855, 48.8648)   # lat
  ),
  data.frame(landmark = factor(c("eiffel_tower", "arc_de_triomphe", 
                                 "notre_dame", "montmartre", "louvre")),
             landmark_name = factor(c("Eiffel Tower", "Arc de Triomphe", 
                                      "Notre Dame", "Montmartre", "The Louvre")))
)

# Create icons
paris_icons <- iconList(
  eiffel_tower = makeIcon("/files/eiffel-tower.png", 28, 28),
  arc_de_triomphe = makeIcon("/files/arc-de-triomphe.png", 20, 20),
  notre_dame = makeIcon("/files/notre-dame.png", 20, 20),
  montmartre = makeIcon("/files/montmartre.png", 20, 20),
  louvre = makeIcon("/files/louvre.png", 25, 25))

```

#### A) Total Airbnb Listings

```{r leaflet-tot-list}
# Set a color palette
col_pal_listings <- colorNumeric(palette = "viridis", domain = paris_merged_sf$n_listings)
# Create labels ->> FIX: change arrondm label from nhood name to arr number
labels_n_listings <- sprintf(
  "<strong>%s</strong><br/> Listings per 1000 people: %g",
  paris_merged_sf$neighbourhood, paris_merged_sf$n_listings) %>% 
  lapply(htmltools::HTML)

# Code for interactive Map
total_listings_map <- paris_merged_sf %>% 
  st_transform(crs = 4326) %>%  # EPSG central france: 27562
  leaflet(width = "100%") %>% 
  addProviderTiles(provider = "CartoDB.Positron") %>% 
  addPolygons(
    #popup = ~paste0(neighbourhood_cleansed, "<br>", "Total listings: ", n_listings),
    label = labels_n_listings,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"), 
      textsize = "12px",
      direction = "auto"),
    stroke = TRUE,
    weight = 1,
    opacity = 10,
    smoothFactor = 0,
    #dashArray = 2,
    fillOpacity = 0.65,
    color = ~col_pal_listings(n_listings),
    highlightOptions = highlightOptions(
      weight = 10,
      color = col_pal_listings, #blackish grey #313130
      #dashArray = "",
      fillOpacity = 0.9,
      bringToFront = TRUE)
  ) %>%
  addLegend(
    "topright",
    title = "Total Listings",
    values = ~n_listings, 
    labFormat = labelFormat(prefix = ""),
    pal = col_pal_listings,
    opacity = 1
  ) %>% 
  addMarkers(
    data = landmarks_coords,
    icon = ~paris_icons[landmark],
    label = ~landmark_name, 
    group = "Landmarks"
    ) %>% 
  addLayersControl(
    overlayGroups = c("Landmarks"),
    options = layersControlOptions(collapsed=FALSE))

#print map
#total_listings_map

# Save interactive map as widget
saveWidget(total_listings_map, file=paste0(getwd(), "/html_widgets/paris_tot_listings.html"))

```

#### B) Airbnb listings by population

```{r leaflet-pop}
# Set a color palette
col_pal_pop <- colorNumeric(palette = "viridis", domain = paris_merged_sf$listings_by_pop)
# Create labels
labels_listings_pop <- sprintf(
  "<strong>%s</strong><br/> Listings per 1000 people: %g",
  paris_merged_sf$arr, paris_merged_sf$listings_by_pop) %>% 
  lapply(htmltools::HTML)


# Code for interactive Map
listings_by_pop_map <- paris_merged_sf %>% 
  st_transform(crs = 4326) %>%  # EPSG central france: 27562
  leaflet(width = "100%") %>% 
  addProviderTiles(provider = "CartoDB.Positron") %>% 
  addPolygons(
    #popup = ~paste0(neighbourhood_cleansed, "<br>", "Listings per 1000 people: ", listings_by_pop),
    label = labels_listings_pop,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"), 
      textsize = "12px",
      direction = "auto"),
    stroke = TRUE,
    weight = 1,
    opacity = 10,
    smoothFactor = 0,
    #dashArray = 2,
    fillOpacity = 0.65,
    color = ~col_pal_pop(listings_by_pop),
    highlightOptions = highlightOptions(
      weight = 10,
      color = col_pal_pop, #blackish grey #313130
      #dashArray = "",
      fillOpacity = 0.9,
      bringToFront = TRUE)
  ) %>% 
  addLegend(
    "topright",
    title = "Listings per <br> 1000 people",
    values = ~listings_by_pop, 
    labFormat = labelFormat(prefix = ""),
    pal = col_pal_pop,
    opacity = 1
  ) %>% 
  addMarkers(
    data = landmarks_coords,
    icon = ~paris_icons[landmark], 
    label = ~landmark_name, 
    group = "Landmarks") %>% 
  addLayersControl(
    overlayGroups = c("Landmarks"),
    options = layersControlOptions(collapsed=FALSE))

#print map
#listings_by_pop_map

# Save interactive map as widget
saveWidget(listings_by_pop_map, file=paste0(getwd(), "/html_widgets/paris_listings_by_pop.html"))
```

#### C) Airbnb listings by square kilometer

```{r leaflet-sqkm}
# Set a color palette
col_pal_km2 <- colorNumeric(palette = "viridis", domain = paris_merged_sf$listings_km2)
# Create labels
labels_listings_km2 <- sprintf(
  "<strong>%s</strong><br/> Listings per km<sup>2</sup>: %g",
  paris_merged_sf$neighbourhood, paris_merged_sf$listings_km2) %>% 
  lapply(htmltools::HTML)

# Code for interactive Map
listings_by_area_map <- leaflet(width = "100%") %>% 
  addProviderTiles(provider = "CartoDB.Positron") %>% 
  addPolygons(data = paris_merged_sf, 
    #popup = ~paste0(neighbourhood_cleansed, "<br>", "Listings per km<sup>2</sup>: ", listings_km2),
    label = labels_listings_km2, 
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"), 
      textsize = "12px",
      direction = "auto"),
    stroke = TRUE,
    weight = 1,
    opacity = 10,
    smoothFactor = 0,
    #dashArray = 2,
    fillOpacity = 0.65,
    color = ~col_pal_km2(listings_km2),
    highlightOptions = highlightOptions(
      weight = 10,
      color = col_pal_km2, #blackish grey #313130
      #dashArray = "",
      fillOpacity = 0.9,
      bringToFront = TRUE)
  ) %>% 
  addLegend(data = paris_merged_sf, 
    "topright",
    title = "Listings <br> per km<sup>2</sup>",
    values = ~listings_km2, 
    labFormat = labelFormat(prefix = ""),
    pal = col_pal_km2,
    opacity = 1
  ) %>% 
  addMarkers(
    data = landmarks_coords, 
    icon = ~paris_icons[landmark], 
    label = ~landmark_name, 
    group = "Landmarks") %>% 
  addLayersControl(
    overlayGroups = c("Landmarks"),
    options = layersControlOptions(collapsed=FALSE))

#print map
#listings_by_area_map

# Save interactive map as widget
saveWidget(listings_by_area_map, file=paste0(getwd(), "/html_widgets/paris_listings_by_area.html"))

```

#### D) Average airbnb price by arrondissement

```{r leaflet-avgprice}
# Set a color palette
col_pal_price <- colorNumeric(palette = "viridis", domain = paris_merged_sf$avg_price)
# Create labels
labels_avg_price <- sprintf(
  "<strong>%s</strong><br/> Average price: $%g",
  paris_merged_sf$neighbourhood, paris_merged_sf$avg_price) %>% 
  lapply(htmltools::HTML)

# Code for interactive Map
listings_price_map <- paris_merged_sf %>% 
  st_transform(crs = 4326) %>%  # EPSG central france: 27562
  leaflet(width = "100%", height = 400) %>%  # height  = 700 ?
  addProviderTiles("CartoDB.Positron", group = "Base 1") %>% # CartoDB.Positron / OpenStreetMap.Mapnik
  addPolygons(data = paris_merged_sf, 
    #popup = ~paste0(neighbourhood_cleansed, "<br>", "Listings per km<sup>2</sup>: ", listings_km2),
    label = labels_avg_price, 
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"), 
      textsize = "12px",
      direction = "auto"),
    stroke = TRUE,
    weight = 1,
    opacity = 10,
    smoothFactor = 0,
    #dashArray = 2,
    fillOpacity = 0.65,
    color = ~col_pal_price(avg_price),
    highlightOptions = highlightOptions(
      weight = 10,
      color = col_pal_price, #blackish grey #313130
      #dashArray = "",
      fillOpacity = 0.9,
      bringToFront = TRUE)
    ) %>% 
  addLegend(
    "topright",
    title = "Average price <br> per night",
    values = ~avg_price, 
    labFormat = labelFormat(prefix = "$ "),
    pal = col_pal_price,
    opacity = 1
    ) %>% 
  addMarkers(
    data = landmarks_coords,
    icon = ~paris_icons[landmark], 
    label = ~landmark_name, 
    group = "Landmarks") %>%
  addLayersControl(
    #baseGroups = c("Base 1", "Base 2", "Base 3", "Base 4", "Base 5"),
    overlayGroups = c("Landmarks"),
    options = layersControlOptions(collapsed=FALSE))

#print map
#listings_price_map

# Save interactive map as widget
saveWidget(listings_price_map, file=paste0(getwd(), "/html_widgets/paris_listings_price.html"))
```

## Data Source

| The [data](http://insideairbnb.com/get-the-data) was sourced from the [Inside Airbnb Project](http://insideairbnb.com/about/) which provides webscraped data for Airbnb listings in cities throughout the globe. The data for Paris was last scraped in June 2022.
